---
title: "Boris Leroy's CV (short version)"
output:
  pdf_document: default
  md_document:
    variant: gfm
    preserve_yaml: true
layout: cv
---



# Boris Leroy
Maitre de Conférences, Muséum National d'Histoire Naturelle

Biology of Aquatic Organisms and Ecosystems<br/>
43 rue Cuvier, CP 26<br/>
75005 Paris, France<br/>

leroy.boris@@gmail.com



[borisleroy.com](https://borisleroy.com) - 
[lab page](https://borea.mnhn.fr/fr/users/boris-leroy) <br/>  
[GitHub: Farewe](https://github.com/farewe) - 
[ORCID: 0000-0002-7686-4302](https://orcid.org/0000-0002-7686-4302) - 
[RG: Boris_Leroy](https://www.researchgate.net/profile/Boris_Leroy) - 
[\@BLeroyEcology](https://twitter.com/BLeroyEcology)

```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(scholar)
id <- "7HzlVT4AAAAJ"

gs <- get_profile(id)

```

*My research focuses on global biogeographical patterns of aquatic biodiversity (marine and freshwater) and their underlying direct and indirect drivers. I investigate with various macroecological and biogeographical methods how global changes alter the natural distribution of biodiversity. My main research topics are: biogeography, macroecology, invasion biology; with a special emphasis on the development of methods and facilitating access to these methods with open-source software. *

## Education
`2012`
**Ph.D., Life Sciences**, *Muséum national d'histoire naturelle/Université de Rennes 1*, Rennes, France

## Experience
`2014-present`
**Maître de conférences (lecturer)**, *Lab. Biology of Aquatic Organisms & Ecosystems, Muséum national d'Histoire Naturelle*, Paris, France.

`2014`
**Post-doctoral fellow**, *UMR 8079 Ecology Systematics & Evolution, University of Paris South XI*, Orsay, France.

`2013`
**Post-doctoral fellow**, *Lab. Biodiversity & Territory Management, University of Rennes 1*, Rennes, France.

## Publications

*[Full Publication list  available by clicking here](https://farewe.github.io/markdown-cv/publications.html).*

### Journal articles
67 published peer-reviewed articles. h-index: `r gs$h_index`; i10-index: `r gs$i10_index`

*Selected publications:*

**Leroy B**, Bellard C, Dias MS, Hugueny B, Jézéquel C, Leprieur F, Oberdorff T, Robuchon M, Tedesco PA. 2023. Major shifts in biogeographic regions of freshwater fishes as evidence of the Anthropocene epoch. *Science Advances* [10.1126/sciadv.adi5502](https://doi.org/10.1126/sciadv.adi5502) --- [HAL](https://hal.science/BOREA/hal-04311267v1)

**Leroy B**. 2023. Choosing presence-only species distribution models. *Journal of Biogeography* 50:247-250 [10.1111/jbi.14505](https://doi.org/10.1111/jbi.14505)  ---  [HAL](https://hal.archives-ouvertes.fr/hal-03813698)

Bernery C, Bellard C, Courchamp F, Brosse S, Gozlan R, Jarić I, Teletchea F, **Leroy B**.  2022. Freshwater fish invasions: A comprehensive review. *Annual Review of Ecology, Evolution and Systematics*  [10.1146/annurev-ecolsys-032522-015551](https://doi.org/10.1146/annurev-ecolsys-032522-015551) ---  [HAL](https://hal.archives-ouvertes.fr/hal-03781186)

**Leroy B**, Kramer AV, Vaissière AC, Kourantidou M, Courchamp F, Diagne C. 2022. Analysing global economic costs of invasive alien species with the invacost R package. *Methods in Ecology & Evolution* 13:1930-1937 [10.1111/2041-210X.13929](https://doi.org/10.1111/2041-210X.13929) ---  [HAL](https://hal.archives-ouvertes.fr/hal-03427555)

### Software
5 software published with 2 peer-reviewed articles, totaling 391 citations

## Expertise
*I work at the science-policy interface, internationally (e.g., **Lead Author** for the European and Central Asia report by the IPBES) or specifically in France (e.g., Terres Australes & Antarctiques Françaises, DREAL Corse).*

19 Expertise reports published in total. Last report:

**Leroy B**. (2024). Cartographie prédictive des habitats des groupes d’espèces ciblées
par les Plans Nationaux d’Actions en Corse. Rapport pour la DREAL de Corse.
Zenodo. 110 pp. https://doi.org/10.5281/zenodo.11067678 https://borisleroy.com/sdms-pna-corse


## Research funding

8 projects funded as PI or co-PI totaling around 1M€. Current projects:

`2023-2026` **3-year research project**, PPR Océan & Climat, Developing bioindicators for rocky foreshores: citizen sciences, a mechanism for interaction between science and society. Co-PI with Eric Feunteun & Florian Charvolin. 110 000€

`2023-2025` **2-year research project**, *Agence Nationale pour la Recherche*,
ESPOIRS - Etude de la réponse des estrans aux changements globaux par les Sciences
Participatives : biOindication à l’InteRface sciences Société. 250 000€. 

## Teaching

Teaching 70-100h per year for masters and doctoral schools at the Muséum and
Ecole Normale Supérieure. Responsibility of two courses:

- \- **Biogeography and Macroecology**, with Maud Mouchet, master's degree course, 10 days.

- \- **Species distribution models and climate change**, doctoral training school, 5 days.

## Supervision & evaluation

6 postdoctoral researchers, 3 PhD students, 2 engineers and 15 master students supervised

Member of 12 PhD committees

Examiner for 3 PhD defenses

## Professional service

Referee for over 25 journals

`2024-present`
**Senior Editor**. *Diversity & Distributions*

`2019-2024`
**Associate Editor**. *Diversity & Distributions*

## Academic service

`2025-onwards`
**Co-leader**, *group AQUATREND, __Quantitative analysis of trends in biodiversity in response to global change__, Lab. Biology of Aquatic Organisms & Ecosystems, Muséum national d'Histoire Naturelle*, Paris, France.


`2017-2019`
**Leader**, *group Biodiversity & Macroecology, Lab. Biology of Aquatic Organisms & Ecosystems, Muséum national d'Histoire Naturelle*, Paris, France.

## Recent outreach events

`2023` **Press** Biological invasions of freshwater fishes and the Anthropocene.
AFP, The Conversation, L'info durable, Presse Agence, France Inter, France Culture (x2), Geo, H20, The Cleveland American, East Africa News Post, Reporterre, Le Figaro, Natura Science. 

`2021`
**Press** Biological invasions, climate change and modelling (Science News, Polytechnique Insights, France TV info, Radio la 1ère//Planète Outre-Mer, Science & Vie)


```{r echo=FALSE, results="hide", message="hide", warning=FALSE} 
Sys.setlocale("LC_ALL","English")
```
<br/>Last updated: `r zoo::Sys.yearmon()`<br/><br/>
