---
output:
  pdf_document:
    latex_engine: pdflatex
header-includes:
  - \usepackage[margin=1in]{geometry}
  - \setlength{\parskip}{5pt}
layout: cv
---



# Boris Leroy
Maitre de Conférences, Muséum National d'Histoire Naturelle

Biology of Aquatic Organisms and Ecosystems<br/>
43 rue Cuvier, CP 26<br/>
75005 Paris, France<br/>

[borisleroy.com](https://borisleroy.com) - 
[lab page](https://borea.mnhn.fr/fr/users/boris-leroy) <br/>  
[GitHub: Farewe](https://github.com/farewe) - 
[ORCID: 0000-0002-7686-4302](https://orcid.org/0000-0002-7686-4302) - 
[RG: Boris_Leroy](https://www.researchgate.net/profile/Boris_Leroy) - 
[\@BLeroyEcology](https://twitter.com/BLeroyEcology)

```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(scholar)
id <- "7HzlVT4AAAAJ"

gs <- get_profile(id)

```

*My research focuses on global biogeographical patterns of aquatic biodiversity (marine and freshwater) and their underlying direct and indirect drivers. I investigate with various macroecological and biogeographical methods how global changes alter the natural distribution of biodiversity. My main research topics are: biogeography, macroecology, invasion biology; with a special emphasis on the development of methods and facilitating access to these methods with open-source software. *

## Education & experience

`2014-present`
**Maître de conférences (lecturer)**, *Lab. Biology of Aquatic Organisms & Ecosystems, Muséum national d'Histoire Naturelle*, Paris

`2014`
**Post-doctoral fellow**, *UMR 8079 Ecology Systematics & Evolution, University of Paris South XI*, Orsay

`2013`
**Post-doctoral fellow**, *Lab. Biodiversity & Territory Management, University of Rennes 1*, Rennes

`2012`
**Ph.D., Life Sciences**, *Muséum national d'histoire naturelle/Université de Rennes 1*, Rennes


## Publications

*[Full Publication list  available by clicking here](https://farewe.github.io/markdown-cv/publications.html).*

### Journal articles
```{r include=FALSE}
source("scripts/count_author_position.R")
pubs <- read_publications("publications.md")
exp <- read_expertise("publications.md")
positions <- count_author_positions(pubs, "\\*\\*Leroy B\\*\\*")
```

`r length(pubs)` published peer-reviewed articles. h-index: `r gs$h_index`; i10-index: `r gs$i10_index`.

Number of papers as 1st author: `r positions$first_author`, 2nd author: `r positions$second_author`, last author: `r positions$last_author`.

*Selected publications:*

Carneiro L, **Leroy B**, Capinha C, Bradshaw CJA, Bertolino S, Catford JA, Camacho-Cervantes M, Bojko J, Klippel G, Kumschick S,  Pinchera-Doñoso D, Tonkin JD, Fath BD, South J, Manfrini E, Dallas T, Courchamp F. **In Press.** Typology of the ecological impacts of biological invasions. *Trends in Ecology & Evolution* 

**Leroy B**, Bellard C, Dias MS, Hugueny B, Jézéquel C, Leprieur F, Oberdorff T, Robuchon M, Tedesco PA. 2023. Major shifts in biogeographic regions of freshwater fishes as evidence of the Anthropocene epoch. *Science Advances* [10.1126/sciadv.adi5502](https://doi.org/10.1126/sciadv.adi5502) --- [HAL](https://hal.science/BOREA/hal-04311267v1)

Ramiro-Sánchez B, Martin A, **Leroy B**. 2023. The epitome of data paucity: Deep-sea habitats of the Southern Indian Ocean. *Biological Conservation* 283:110096 [doi](https://doi.org/10.1016/j.biocon.2023.110096) --- [HAL](https://hal.science/hal-04554845)


**Leroy B**, Kramer AV, Vaissière AC, Kourantidou M, Courchamp F, Diagne C. 2022. Analysing global economic costs of invasive alien species with the invacost R package. *Methods in Ecology & Evolution* 13:1930-1937 [10.1111/2041-210X.13929](https://doi.org/10.1111/2041-210X.13929) ---  [HAL](https://hal.archives-ouvertes.fr/hal-03427555)

### Software

```{r include=FALSE}
source("scripts/citation_count.R")
library(dplyr)
info <- available.packages(contriburl = "https://cran.rstudio.com/src/contrib")



softs <- read_software("publications.md")

# Split the raw text into individual entries based on blank lines
entries <- unlist(str_split(softs, "\\n\\s*\\n"))

# Apply the parsing function to each entry and combine into a data.frame
software_list <- do.call(rbind, lapply(entries, parse_entry))

software_list <- software_list %>%
  rowwise() %>%
  mutate(
    # citations_software = get_google_scholar_citation(software_url),
    citations_peer_review = fetch_semantic_scholar_citations(doi_peer_review),
    total_citations = 
      # citations_software + 
      citations_peer_review
  ) %>%
  ungroup()

total_dois <- sum(sapply(software_list$doi_peer_review, function(x) {
  if (is.na(x) || x == "") 0 else length(unlist(strsplit(x, ";")))
}))

```

`r nrow(software_list)` software published with 
`r total_dois` peer-reviewed articles, totaling over 
`r sum(software_list$total_citations, na.rm = TRUE)` citations.

## Expertise
I work at the science-policy interface as part of my expertise mission from the MNHN.

`2024` **Consultant**, *DREAL Corse*, Predictive mapping of species subject to national action plans

`2020-2023` **Consultant**, *Southern Indian Ocean Fisheries Agreement*, Vulnerable Marine Ecosystems 

`2021` **Consultant**, *Marine protected areas in the French Antarctic and Southern areas*

`2020-2023`
**Contributing Author**, *Intergovernmental Platform on Biodiversity & Ecosystem Services*, Invasive Alien Species Assessment

`2015-2018`
**Lead Author**, *Intergovernmental Platform on Biodiversity & Ecosystem Services*, Europe and Central Asia Assessment


**`r length(exp)`** expertise reports published. Selected recent expertise reports:

`2024`

**Leroy B**. (2024). Cartographie prédictive des habitats des groupes d’espèces ciblées
par les Plans Nationaux d’Actions en Corse. Rapport pour la DREAL de Corse.
Zenodo. 110 pp. https://doi.org/10.5281/zenodo.11067678

`2023`

Ramiro-Sánchez B., Devillers R. and **Leroy B**. (2023). Systematic conservation planning in the SIOFA area (Project PAE2021-01). Muséum National d’Histoire Naturelle, France. 56pp. [Note: report is confidential]

Ramiro-Sanchez B. and **Leroy B**. (2023). Identifying significant adverse impacts on vulnerable marine ecosystems: a review of measures and applicability to SIOFA (Project PAE2021-01). Muséum National d’Histoire Naturelle, France. 12pp. [Note: report is confidential]

`2022`

Ramiro-Sánchez B, **Leroy B**. 2022. *SIOFA bioregionalisation and VME project - Final report* Southern Indian Ocean Fisheries Agreement consultancy report. 111 pp. [link](https://siofa.org/sites/default/files/files/VMEMapping_FullReport.pdf)

## Research funding

8 projects funded as PI or co-PI totaling around 1M€. Recent projects:

`2023-2026` **3-year research project**, PPR Océan & Climat, Developing bioindicators for rocky foreshores: citizen sciences, a mechanism for interaction between science and society. Co-PI with Eric Feunteun & Florian Charvolin. 110 000€

`2023-2025` **2-year research project**, *Agence Nationale pour la Recherche*,
ESPOIRS - Etude de la réponse des estrans aux changements globaux par les Sciences
Participatives : biOindication à l’InteRface sciences Société. 250 000€. 

`2021-2023` **1.5-year research project**, *Southern Indian Ocean
Fisheries Agreement*, Indian Ocean, 60 000€. <br/> Bioregionalisation and 
Management of Vulnerable Marine Ecosystems in the Indian
Ocean.

`2021` **Expertise project**, *Planification de l'extension de la réserve Naturelle de Saint Paul et Amsterdam*, Terres Australes et Antarctiques Françaises, ~20k€.

`2020-2022`
**2-year research project**, *Southern Indian Ocean Fisheries Agreement*, Indian Ocean, 96 000€. <br/> 
Mapping the biogeography of Vulnerable Marine Ecosystems in the Indian Ocean.

`2017–2019`
**2-year research project Labex**, *Muséum National d'Histoire Naturelle*, France, 100 000€. <br/>
Co-PI with Sarah Samadi & Maud Mouchet.<br/>
Valuing natural history collections and naturalist expeditions for the conservation and management of deep sea habitats: the Tropical Deep Sea Benthos program.

`2017–2019`
**2-year research project Labex**, *Muséum National d'Histoire Naturelle*, France, 100 000€.<br/> Co-PI with Sandrine Pavoine.<br/>
New indicators for biodiversity conservation based on phylogenetic originality and extinction risks : HEDGE and LEDGE species.

## Teaching

Teaching 70-100h per year for masters and doctoral schools at the Muséum, Sorbonne Université, Université de Paris Saclay, and Ecole Normale Supérieure. 

## Supervision & evaluation

6 postdoctoral researchers, 3 PhD students, 2 engineers and 15 master students supervised

Member of 12 PhD committees

Examiner for 5 PhD defenses

## Professional service

Referee for over 25 journals

`2024-present`
**Senior Editor**. *Diversity & Distributions*

`2019-2024`
**Associate Editor**. *Diversity & Distributions*

## Academic service

`2025-onwards`
**Co-leader**, *group AQUATREND, __Quantitative analysis of trends in biodiversity in response to global change__, Lab. Biology of Aquatic Organisms & Ecosystems, Muséum national d'Histoire Naturelle*, Paris, France.


`2017-2019`
**Leader**, *group Biodiversity & Macroecology, Lab. Biology of Aquatic Organisms & Ecosystems, Muséum national d'Histoire Naturelle*, Paris, France.

## Outreach

Numerous outreach/press events around global change impacts on biodiversity
(AFP, The Conversation, France Inter, France Culture, etc.)


```{r echo=FALSE, results="hide", message="hide", warning=FALSE} 
Sys.setlocale("LC_ALL","English")
```
<br/>Last updated: `r zoo::Sys.yearmon()`<br/><br/>
